scRNAseq benchmark in want of a title

### 2020-01-23 bmc_article.tex
Updates from Overleaf

Single-cell RNA-sequencing (scRNAseq) and the set of attached analysis methods are evolving fast, and while a number of good comparison/benchmark studies can inform analytical decisions (\citealp{duoClustering2018}, etc) they need constant updating and often leave open many details of an analysis. Here, we go in more detail on the various steps of analysis leading from an initial count matrix to a cluster assignment, which are critical steps in a wide range of applications. We harness real datasets of known cell composition (Table \ref{tab:table1}) and develop new evaluation metrics to investigate in a multilevel fashion the impact of various parameters and variations around a core scRNAseq pipeline.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{figure0}
    \caption{\textbf{Overview of the pipeComp framework and its application to a scRNAseq clustering pipeline.}}
    \label{fig:figure2}
\end{figure}

@@

In addition to these methods, we reasoned that an approach such as \texttt{DoubletFinder} could be simplified by being applied directly on counts and by using a pre-clustering to create neotypic doublets (i.e. doublets from different cell types) more efficiently. We therefore developed a simple and fast package implementing this for doublet detection, with the added advantage of accounting for uncertainty in the expected doublet rate and using meta-cells from the clusters to even include triplets (see methods).

>>>>

Single-cell RNA-sequencing (scRNAseq) and the set of attached analysis methods are evolving fast, and while a number of good comparison/benchmark studies can inform analytical decisions (\citealp{duoClustering2018, SonesonDE2018, SunDimRed2019}) they need constant updating and often leave open many details of an analysis. Here, we go in more detail on the various steps of analysis leading from an initial count matrix to a cluster assignment, which are critical steps in a wide range of applications. We harness real datasets of known cell composition (Table \ref{tab:table1}) and develop new evaluation metrics to investigate in a multilevel fashion the impact of various parameters and variations around a core scRNAseq pipeline.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{main_figures/pipeline_explanation.png}
    \caption{\textbf{Overview of the pipeComp framework and its application to a scRNAseq clustering pipeline.}}
    \label{fig:figure2}
\end{figure}

@@

In addition to these methods, we reasoned that an approach such as \texttt{DoubletFinder} could be simplified by being applied directly on counts and by using a pre-clustering to create neotypic/heterotypic doublets (i.e. doublets from different cell types) more efficiently. We therefore developed a simple and fast package implementing this for doublet detection, with the added advantage of accounting for uncertainty in the expected doublet rate and using meta-cells from the clusters to even include triplets (see methods).
